1. Open the diamonds dataset
```{r}
library(ltm)
library(ggplot2)
data(diamonds)

```
2. What would be the appropriate correlation to calculate to determine the relationship between clarity and price? Explain you reasoning
```{r}
View(diamonds)
### I would use ANOVA because we're trying to find the difference between categorical data (clarity) and price (continuous).###
```
3. Calculate the correlation you chose in #2. (Hint: you may need ot change a class of variable)
```{r}
as.factor(diamonds$clarity)
diamondAnova<-lm(price~clarity, data=diamonds)
diamondAnova
```
4. Calculate a spearman's rho and a kendall's tau for the relationship between carat and clarity. What do you notice about the results?
```{r}
cor.test(diamonds$carat, diamonds$clarity, method = "spearman")
cor.test(diamonds$carat, diamonds$clarity, method = "kendall")

```
5. Use a wilcoxen test to compare the price of "premium" diamonds and "very good" diamonds. How does this compare to the results of a t test?
```{r}
colnames(diamonds)
wilcox.test(cut~price, data=diamonds)
```

6. For the following questions, use the following scenario: 
You are given a 25 question test that you didn't study for and got 15 correct. If you were to completely guess on all questions, would you do better than chance if: 

a) it was all true/false questions

b) it was multiple choice and all questions had 3 choices

c) it was multiple choice and all questions had 4 choices

7) open the HairEyeColor dataset
```{r}
data(HairEyeColor)
HairEyeColor<-as.data.frame(HairEyeColor)
```

8) Does red hair occur more often than chance? 

9) Do Hazel eyes occur more often than chance?




